Describing the C-space of asynchronous periodic task using DIT

### 2013-07-23 dit-paper.tex
Begun to copypaste some text

The method used to generate the system consisted of
\begin{itemize}
	\item Generating the $U_i$ with the \texttt{UUniSort} algorithm described in \cite{bini2005measuring}, with parameters
	\begin{itemize}
		\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
		\item $n$ (number of tasks) chosen uniformly between 1 and 4
	\end{itemize}
	\item Generating the $T_i$ from a list of divisors (see \ref{sct:simuRemarks}). This also gives the $C_i = \lfloor U_i \, T_i \rfloor$
	\item $O_i$ (...)
	\item And finally, choosing the $D_i$ uniformly in the interval $[T_i - \frac{T_i - C_i}{e}, T_i)$, where the value of $e$ is discussed in \ref{sct:simuRemarks}.
\end{itemize}

>>>>

The method used to generate the system consisted of
\begin{itemize}
	\item Generating the $U_i$ with the \texttt{UUniSort} algorithm described in \cite{bini2005measuring}, with parameters
	\begin{itemize}
		\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
		\item $n$ (number of tasks) chosen uniformly between 1 and 4
	\end{itemize}
	\item Generating the $T_i$ from a list of divisors (see \ref{sct:simuRemarks}). This also gives the $C_i = \lfloor U_i \, T_i \rfloor$
	\item $O_i$ (...)
	\item And finally, choosing the $D_i$ uniformly in the interval $[T_i - \frac{T_i - C_i}{e}, T_i]$, where the value of $e$ is discussed in \ref{sct:simuRemarks}.
\end{itemize}

### 2013-07-23 dit-paper_ieee.tex

		This system is guaranteed to have at least one solution modulo $H$ for given
		values of $a_i$ if the following condition is respected:
		\[
			a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
			T_j)) \; \forall i,j
		\]
		which means that there could be systems with no first periodic DIT.

@@

  (Work in Progress...)

  `e' factor...

>>>>

		This system is guaranteed to have at least one solution modulo $H$ for given
		values of $a_i$ if the following condition is respected:
		\[
			a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
			T_j)) \; \forall i,j
		\]
		which means that there could be systems with no first periodic DIT.
		We now present an example of such a system.\\

		\begin{center}
		\begin{tabular}{|r|c|c|c|c|}
		 \hline
		  & $O_i$ & $C_i$ & $D_i$ & $T_i$ \\
		 \hline
		 $\tau_1$ & 0 & $C_1$ & 3 & 4\\
		 \hline
		 $\tau_2$ & 2 & $C_2$ & 7 & 8\\
		 \hline
		\end{tabular}
		\end{center}
		~\\

		Here, the possible values of $a_1$ are 3 and 4, and the possible values
		of $a_2$ are 7 and 8. For a first periodic DIT to exist, one of those
		condition must be fulfilled:
		\[
		\left[
		\begin{array}{c}
			3 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
			3 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
			4 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
			4 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
		\end{array}
		\right.
		\]
		However those four conditions are false, so the system has no first
		periodic DIT (and no other DIT than $t=0$).

@@

	We wanted to quantify how much systems has a first periodic DIT........

	We generated task systems by
	\begin{itemize}
		\item Generating utilization values with the \texttt{UUniSort} algorithm described in \cite{bini2005measuring}, with parameters
		\begin{itemize}
			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
			\item $n$ (number of tasks) equal to 3
		\end{itemize}
		\item Choosing the $T_i$ uniformly between 5 and 20, which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
		\item Choosing the $D_i$ uniformly in the interval $[T_i - \frac{T_i - C_i}{CDF}, T_i]$, where the $CDF$ is called \emph{Constrained Deadline Factor}.
	\end{itemize}
	and then computed the value of the first periodic DIT.\\

	We use the CDF because........

	The result are represented in Fig. \ref{fig:noFPDIT}

	\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{python-simulation/plots/nofpdit.png}
	\end{center}
	\label{fig:noFPDIT}
	\end{figure}
